\begin{thebibliography}{00}



\bibitem{cloud}
Armbrust, Michael, Armando Fox, Rean Griffith, Anthony D. Joseph, Randy Katz, Andy Konwinski, Gunho Lee et al. "A view of cloud computing." \emph{Communications of the ACM} 53.4 (2010): 50-58.
\bibitem{spark}
Zaharia, Matei, Mosharaf Chowdhury, Michael J. Franklin, Scott Shenker, and Ion Stoica. "Spark: cluster computing with working sets." \emph{Proceedings of the 2nd USENIX conference on Hot topics in cloud computing}. 2010.
\bibitem{rdd}
Zaharia, Matei, Mosharaf Chowdhury, Tathagata Das, Ankur Dave, Justin Ma, Murphy McCauley, Michael J. Franklin, Scott Shenker, and Ion Stoica. "Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing." \emph{Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation}. USENIX Association, 2012.
\bibitem{bigdata}
Wu, Xindong, Xingquan Zhu, Gong-Qing Wu, and Wei Ding. "Data mining with big data." \emph{Knowledge and Data Engineering}, IEEE Transactions on 26.1 (2014): 97-107.
\bibitem{cloudopt}
Chaisiri, Sivadon, Bu-Sung Lee, and Dusit Niyato. "Optimization of resource provisioning cost in cloud computing." \emph{Services Computing}, IEEE Transactions on 5.2 (2012): 164-177.
\bibitem{cloudscale}
Patel, Parveen, Deepak Bansal, Lihua Yuan, Ashwin Murthy, Albert Greenberg, David A. Maltz, Randy Kern et al. "Ananta: Cloud scale load balancing." \emph{ACM SIGCOMM Computer Communication Review}. Vol. 43. No. 4. ACM, 2013.

\bibitem{dbseer}
Mozafari, Barzan, Carlo Curino, and Samuel Madden. "DBSeer: Resource and Performance Prediction for Building a Next Generation Database Cloud." \emph{CIDR}. 2013.


\bibitem{prepare}
Tan, Yongmin, Hiep Nguyen, Zhiming Shen, Xiaohui Gu, Chitra Venkatramani, and Deepak Rajan. "Prepare: Predictive performance anomaly prevention for virtualized cloud systems." \emph{Distributed Computing Systems (ICDCS), 2012 IEEE 32nd International Conference on. IEEE}, 2012.



\bibitem{crossp}
Heintz, Benjamin, Abhishek Chandra, and Jon Weissman. "Cross-phase optimization in MapReduce." \emph{Cloud Computing for Data-Intensive Applications}. Springer New York, 2014. 277-302.
\bibitem{stat}
Ganapathi, Archana, Yanpei Chen, Armando Fox, Randy Katz, and David Patterson. "Statistics-driven workload modeling for the cloud." \emph{Data Engineering Workshops (ICDEW)}, 2010 IEEE 26th International Conference on. IEEE, 2010.
\bibitem{predict}
Popescu, Adrian Daniel, Andrey Balmin, Vuk Ercegovac, and Anastasia Ailamaki. "PREDIcT: towards predicting the runtime of large scale iterative analytics." \emph{Proceedings of the VLDB Endowment} 6.14 (2013): 1678-1689.
\bibitem{oltp}
Mozafari, Barzan, Carlo Curino, Alekh Jindal, and Samuel Madden. "Performance and resource modeling in highly-concurrent oltp workloads." \emph{Proceedings of the 2013 ACM SIGMOD International Conference on Management of Data}. ACM, 2013.
\bibitem{starfish}
Herodotou, Herodotos, Harold Lim, Gang Luo, Nedyalko Borisov, Liang Dong, Fatma Bilgen Cetin, and Shivnath Babu. "Starfish: A Self-tuning System for Big Data Analytics." \emph{CIDR}. Vol. 11. 2011.
\bibitem{nosqlmodel}
Barbierato, Enrico, Marco Gribaudo, and Mauro Iacono. "Performance evaluation of nosql big-data applications using multi-formalism models." \emph{Future Generation Computer Systems} 37 (2014): 345-353.
\bibitem{pmodel}
Zhang, Zhuoyao, Ludmila Cherkasova, and Boon Thau Loo. "Performance modeling of mapreduce jobs in heterogeneous cloud environments." \emph{Proceedings of the 2013 IEEE Sixth International Conference on Cloud Computing}. IEEE Computer Society, 2013.
\bibitem{amml}
Didona, Diego, Francesco Quaglia, Paolo Romano, and Ennio Torre. "Enhancing Performance Prediction Robustness by Combining Analytical Modeling and Machine Learning." \emph{Proceedings of the International Conference on Performance Engineering (ICPE)}. ACM. 2015.
\bibitem{hadoop}
Apache Hadoop. [Online]. Available: \url{https://hadoop.apache.org/}
\bibitem{mr}
Dean, Jeffrey, and Sanjay Ghemawat. "MapReduce: simplified data processing on large clusters." \emph{Communications of the ACM} 51.1 (2008): 107-113.
\bibitem{datampi}
Liang, Fan, Chen Feng, Xiaoyi Lu, and Zhiwei Xu. "Performance benefits of DataMPI: a case study with BigDataBench." \emph{Big Data Benchmarks, Performance Optimization, and Emerging Hardware}. Springer International Publishing, 2014. 111-123.
\bibitem{hive}
Apache Hive ${}^{TM}$. [Online]. Available: \url{https://hive.apache.org/}
\bibitem{hdfs}
Shvachko, Konstantin, Hairong Kuang, Sanjay Radia, and Robert Chansler. "The hadoop distributed file system." \emph{Mass Storage Systems and Technologies (MSST)}, 2010 IEEE 26th Symposium on. IEEE, 2010.
\bibitem{exetime}
Wu, Wentao, Yun Chi, Hakan Hacígümüs, and Jeffrey F. Naughton. "Towards predicting query execution time for concurrent and dynamic database workloads." \emph{Proceedings of the VLDB Endowment} 6.10 (2013): 925-936.
\bibitem{ppredict}
Duggan, Jennie, Ugur Cetintemel, Olga Papaemmanouil, and Eli Upfal. "Performance prediction for concurrent database workloads." \emph{Proceedings of the 2011 ACM SIGMOD International Conference on Management of data}. ACM, 2011.
\bibitem{mempredict}
Li, Ang, Xuanran Zong, Srikanth Kandula, Xiaowei Yang, and Ming Zhang. "CloudProphet: towards application performance prediction in cloud." \emph{ACM SIGCOMM Computer Communication Review}. Vol. 41. No. 4. ACM, 2011.
\bibitem{mrsample}
Grover, Raman, and Michael J. Carey. "Extending map-reduce for efficient predicate-based sampling." \emph{Data Engineering (ICDE), 2012 IEEE 28th International Conference} on. IEEE, 2012.
\bibitem{json}
JSON. [Online]. Available: \url{http://json.org/}
\bibitem{sdss}
Sloan Digital Sky Survey. [Online]. Available: \url{http://www.sdss.org/}
\bibitem{snap}
Stanford SNAP. [Online]. Available: \url{http://snap.stanford.edu/}




\end{thebibliography}







