\documentclass[10pt, conference, compsocconf]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{caption}
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage{soul}


\begin{document}

\title{Performance Prediction for Apache Spark Platform}


\author{\IEEEauthorblockN{Kewen Wang}
\IEEEauthorblockA{Department of Computer Science and Engineering\\
University of Connecticut, Storrs, Connecticut, USA\\
kewen.wang@uconn.edu}
\and
\IEEEauthorblockN{Mohammad Maifi Hasan Khan}
\IEEEauthorblockA{Department of Computer Science and Engineering\\
University of Connecticut, Storrs, Connecticut, USA\\
maifi.khan@engr.uconn.edu}}

\maketitle

\begin{abstract}
Apache Spark is an open source distributed data processing platform that uses distributed memory abstraction to process large volume of data efficiently. However, performance of a particular job on Apache Spark platform can vary significantly depending on the input data type and size, design and implementation of the algorithm, and computing capability, making it extremely difficult to predict the performance metric of a job such as execution time, memory footprint, and I/O cost. To address this challenge, in this paper, we present a simulation driven prediction model that can predict job performance with high accuracy for Apache Spark platform. Specifically, as Apache spark jobs are often consist of multiple sequential stages, the presented prediction model simulates the execution of the actual job by using only a fraction of the input data, and collect execution traces (e.g., I/O overhead, memory consumption, execution time) to predict job performance for each execution stage individually. We evaluated our prediction framework using four real-life applications on a 13 node cluster, and experimental results show that the model can achieve high prediction accuracy.


\end{abstract}
\begin{IEEEkeywords}
Apache Spark; Performance Modeling; Execution Time Prediction
\end{IEEEkeywords}


\IEEEpeerreviewmaketitle




\input{introduction}
\input{related}
\input{overview}
\input{evaluation}
\input{conclusion}



\section*{Acknowledgment}
\noindent
This work is supported by the AFOSR under Grant No. FA 9550-15-1-0184. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the funding agency. %We would also like to thank the Sloan Digital Sky Survey Participating Institutions for providing the numerical Color-Magnitude Diagram data of galaxy, and Stanford SNAP group for sharing the network dataset of the online blogging community LiveJournal.




\bibliographystyle{IEEEtran}
\bibliography{main}


\end{document}


