


\newcommand{\nop}[1]{}
\documentclass[conference]{IEEEtran}

\usepackage{amsmath}
\usepackage[belowskip=-6pt,aboveskip=0pt]{caption}
\usepackage[lined,linesnumbered,noresetcount]{algorithm2e}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{url}
  
\usepackage{caption}
\usepackage{mathtools}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}









\ifCLASSINFOpdf
 
\else
 
\fi






\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}


\title{Modeling Interference for Apache Spark Jobs}



\author{\IEEEauthorblockN{Kewen Wang, Mohammad Maifi Hasan Khan, Nhan Nguyen and Swapna Gokhale}
\IEEEauthorblockA{Department of Computer Science and Engineering\\
University of Connecticut\\ Email: kewen.wang@uconn.edu, maifi.khan@engr.uconn.edu,nhan.q.nguyen@uconn.edu,ssg@engr.uconn.edu}}


\maketitle


\begin{abstract}

To maximize resource utilization and system throughput, hardware resources are often shared across multiple Apache Spark jobs through virtualization techniques in cloud platforms. However, while the performance of these jobs running in virtualized environment can be negatively affected due to interference caused by resource contention, it is nontrivial to predict the effect of interference on job performance in such settings, which is critical for efficient scheduling of such jobs and performance troubleshooting. To address this challenge, in this paper, we develop analytical models to estimate the effect of interference among multiple Apache Spark jobs running concurrently on job execution time in virtualized cloud environment. We evaluated the accuracy of our models using four real-life applications (e.g., Page rank, K-means, Logistic regression, and Word count) on a 6 node cluster while running up to four jobs concurrently. Our experimental results show that the model can achieve high prediction accuracy, and ranges between 86\% to 99\% when the number of concurrent jobs are four and all start simultaneously, and ranges between 71\% to 99\% when the number of concurrent jobs are four and start at different times.


 



\end{abstract}

\begin{IEEEkeywords}

Apache Spark; Modeling Performance Interference; Execution Time Prediction

\end{IEEEkeywords}


\IEEEpeerreviewmaketitle

\input{introduction}
\input{related}
\input{overview}
\input{evaluation}
\input{newsection}
\input{limitations}
\input{conclusion}


\section{Acknowledgement} 
This work is supported by the AFOSR under Grant No.
\linebreak FA 9550-15-1-0184. Any opinions, findings, and conclusions
or recommendations expressed in this material are those of
the authors and do not necessarily reflect the views of the
funding agency.


\bibliographystyle{IEEEtran}
\bibliography{paper}


\end{document}


